Introduction

### 2024-12-04 choose_license.qmd
Various minor stylistic and typographic improvements

- __Attribution__ means whether recipients of your work are required to provide attribution to you. For software licenses, the attribution is part of a copyright notice. Note that even if attribution is not a requirement of the license, good scientific practice demands that appropriate citations are made.
- __State changes__ means that recipients need to indicate if changes were made.
- __Anti-DRM__ means that when others share your work they are not allowed to apply technological measures restricting anything that the license permits. DRM is an abbreviation for **d**igital **r**ights **m**anagement.

@@

However, applying a restriction such as only permitting non-commercial use or not allowing derivative works creates _silos_ of works which are mutually incompatible with each other. Put differently, one cannot share a remix of two works where one is licensed under CC\ BY-SA\ 4.0 and the other only allows non-commercial use. In order to avoid silos, one should only choose license which are compatible with the dominant copyleft license in the respective community [@Lammerhirt2017; @Wheeler2014]. If you would like to learn more about the different types of compatibility, we recommend you to read the article "A Quick Guide to Software Licensing for the Scientist-Programmer" by @Morin2012. The following diagram provides an overview of the compatibility of various licenses:

!["Open data-capable license interoperability" by Robbie Morrison licensed under [CC\ BY\ 4.0](https://creativecommons.org/licenses/by/4.0/). Taken without modification from @Morrison2024](images/Morrison2024.jpg){.lightbox}
:::

@@

Having selected the licenses of your choice -- again, you might need multiple ones depending on the types of works your project contains --, we encourage you to read through the full license text (or at least a legal summary) to understand their effect. Then, you can record the license of existing content and apply the licenses of your own contributions. Mostly, this just means indicating which license applies to which file or folder, usually in the project's README (among other places), whose creation will be discussed [later](make_readme.qmd).

>>>>

- __Attribution__ means whether recipients of your work are required to provide attribution to you. For software licenses, the attribution is part of a copyright notice. Note that even if attribution is not a requirement of the license, good scientific practice demands that appropriate citations are made.
- __State changes__ means that recipients need to indicate if changes were made.
- __Anti-DRM__ means that when others share your work they are not allowed to apply technological measures restricting anything that the license permits. Implementing such restrictive measures is also referred to as **d**igital **r**ights **m**anagement (DRM).

@@

However, applying a restriction such as only permitting non-commercial use or not allowing derivative works creates _silos_ of works which are mutually incompatible with each other. Put differently, one cannot share a remix of two works where one is licensed under CC\ BY-SA\ 4.0 and the other only allows non-commercial use. In order to avoid silos, one should only choose licenses which are compatible with the dominant copyleft license in the respective community [@Lammerhirt2017; @Wheeler2014]. If you would like to learn more about the different types of compatibility, we recommend you to read the article "A Quick Guide to Software Licensing for the Scientist-Programmer" by @Morin2012. The following diagram provides an overview of the compatibility of various licenses:

!["Open data-capable license interoperability" by Robbie Morrison [-@Morrison2024] licensed under [CC\ BY\ 4.0](https://creativecommons.org/licenses/by/4.0/)](images/Morrison2024.jpg){.lightbox}
:::

@@

Having selected the licenses of your choice -- again, you might need multiple ones depending on the types of works your project contains --, we encourage you to read through the full license text (or at least a legal summary) to understand their effect. Then, you can record the license of existing content and apply the licenses of your own contributions. Mostly, this just means indicating which file or folder is covered by which license, usually in the project's README (among other places), whose creation will be discussed [later](make_readme.qmd). Notably, no sort of registration is required.

### 2024-12-04 intro.qmd
Use global language and tidy _quarto.yml
Various minor stylistic and typographic improvements

---
title: "Introduction"
lang: en
---

@@

Even for articles that are use computers to apply existing methods (rather than reporting on a new method), sharing the source code and being transparent about the computational environment is imperative to making research reproducible [@Ince2012]. By reproducibility, we mean "obtaining consistent results using the same input data; computational steps, methods, and code; and conditions of analysis" [@NASEM2019, p. 46].

@@

The practice to interleave narrative text with code has its roots in the paradigm of literate programming, where documentation and source code are treated as equals and are arranged in a way to maximize understanding [@Knuth1984]. Alternating text and code can be also found in notebook interfaces for exploratory programming, such as provided by Wolfram Mathematica or Jupyter Notebooks [@Kluyver2016], with the added capability of executing the code and embedding its output. With _Sweave_ [@Leisch2002], ideas from both worlds -- literate programming and embedding program output -- were combined into one tool for rendering dynamic documents using the R programming language. It is the predecessor of the R package `knitr` [@Xie2015] which is being used under the hood in this tutorial.^[Specifically, Quarto employs `knitr` to execute chunks of R code.]

>>>>

---
title: "Introduction"
---

@@

Even when researchers merely apply existing methods (rather than report on a new method), sharing the source code and being transparent about the computational environment is imperative to making their results reproducible [@Ince2012]. By reproducibility, we mean "obtaining consistent results using the same input data; computational steps, methods, and code; and conditions of analysis" [@NASEM2019, p. 46].

@@

The practice to interleave narrative text with code has its roots in the paradigm of literate programming, where documentation and source code are treated as equals and are arranged in a way to maximize understanding [@Knuth1984]. Alternating text and code can be also found in notebook interfaces for exploratory programming [e.g., Wolfram Mathematica or Jupyter Notebooks, see @Kluyver2016] that also have the capability to execute code and embed its output. With _Sweave_ [@Leisch2002], ideas from both worlds -- literate programming and embedding program output -- were combined into one tool for rendering dynamic documents using the R programming language. It is the predecessor of the R package `knitr` [@Xie2015] which is being used under the hood in this tutorial.^[Specifically, Quarto employs `knitr` to execute chunks of R code.]
